Co-citations in context

### 2019-06-04 cocit_r.tex
More revision from 6/4

@@

Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the observed disciplinary makeup of citation in practice. \emph{More needed here}  Here is Sitaram's study:

Adding to the point of papers citing papers belonging to the same discipline, I collected the subject areas for all the cited references from the 1985 Applied Physics dataset and searched for the keyword `Physics`. Then calculated the percentage of references related to Applied Physics for each paper References-related-to-physics/Total-references. Only papers with at-least 5 references were considered and the total publications were 6991.
Results show a mean of 0.77 i.e. on an average papers cite 77\% of their references belonging to same discipline.

\noindent count    6991.000000\\
mean        0.774002

@@

Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model. A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references. We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.  \emph{Insert comment about the left-hand side of Figure \ref{fold_effect} where the disciplinary dataset has resolved the fold issue.}  We also predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset. The results in Table \ref{tab:KLD} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).

@@

Contrary to Uzzi et al. we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty. Thus, with this lack of robustness, studies are faced with the necessity of defining which parameters are the best parameters to classify articles.

>>>>

\emph{Text from George that may serve well with, or in place of the above as an introduction to this subsection.}  Like Uzzi et al., we also used a Monte Carlo approach to simulate under a random graph model. A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references. We addressed this consideration by analyzing disciplinary subsets of the scientific literature, thereby restricting random selection of references to only those references in the disciplinary network being studied.

@@

Another possible symptom of model misspecification is that random sampling of citations associated with an article do not match with the distribution of citations across the disciplines observed in articles from that discipline. \citep{wallace_lariviere_gingras_2012} found that, often, a majority of an article's citations are the specialty of the article, although the percentage of citations from the same disciplinary focus varied among disciplines in the eight specialties they investigated: from approximately 39\% to 89\% in 2006. \emph{More needed here}  Similarly, we found that 77.4\% of citation in applied physics articles in 1985 (replace with 1995 data?) were from applied physics.  \emph{Add references to other datasets.} A random sampling of citations would ideally reflect the percentages from the discipline in question, as well as the percentages of articles from other discipline.

@@

\emph{Insert comment about the left-hand side of Figure \ref{fold_effect} where the disciplinary dataset has resolved the fold issue.}  We also predicted that model misspecification as measured by the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies in a disciplinary network would be less than the divergence for observed and simulated frequencies in the WoS superset. The results in Table \ref{tab:KLD} indicate that for the set of journals common to both a disciplinary network and the WoS superset, simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset (and its attendant substitutions that are ectopic with respect to field and discipline).

@@

Contrary to Uzzi et al. we found the category displaying the highest hit rate to be sensitive to the experimental parameter settings, which included the percentage of articles deemed to be hits and the percentile of articles' z-score distributions that delineated between articles of low novelty and high novelty. Faced with this lack of robustness, we are confronted with the necessity of defining defendable parameters, if possible, that determine novelty and conventionalty. More significantly, we should question whether the simple approach of defining novelty and conventionality as is done this article and other research is sufficient or whether we should expect such variation in the factors associated with impact as we have observed.
